\texttt{TREE}: A package for modelling plant TRait Ecology and Evolution

### 2015-05-28 ms.tex
Reorganise schematic figures, and all figures generally
output -> figures
schematic is contained within figures

Fixes #22

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{output/plant.pdf}
\caption{Physiological dynamics for individual plants vary with size, trait
and light environment. (a) Growth trajectories for plants differing in light
environment and trait (LMA, low = 0.1, solid line; high =  0.267, dashed
line). Lower light environments slow trajectories and interact non-linearly
with traits. (b) Over time, the fraction of living tissue switches from leaf
towards sapwood, with high LMA species having relatively more mass in leaf
than low LMA species. (c) Growth rates peak around 5m high, but this position
varies with both trait and light level (note that this is the derivative of
panel (a)). (d) Growth rates vary with plant size (seedling and mature shown)
and with traits; growth rate differences are more pronounced in high light.
Whole plant light compensation points emerge from the model as the point where
growth rate is zero (x intercept).  The light level used in panels (a) and (c)
is indicated with dots.}
\label{fig:plant}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{output/patch.pdf}
\caption{Population dynamics for two species competing within a patch. Lines
in panels (a) and (b) show the growth trajectories for individuals on the
boundary of successive "cohorts" for each species. A single cohort includes
all individuals born within a given time period. Red lines are the low LMA
species from figure \ref{fig:plant}, blue lines are the high LMA species.  The
initial growth rate advantage of the low LMA species (see Figure
\ref{fig:plant} c) means it quickly over tops the high LMA species,
suppressing its growth.  Self-thinning leaves space for the high LMA species
to establish below the canopy of the fast species. Panel (a) shows all
trajectories equally weighted; the spacing is generated by an adaptive
refinement algorithm.  In panel (b) trajectories are shaded by the density of
individuals at given size and patch age.  (c) The leaf area index at ground
level for each species.  The dotted line is the total leaf area index (sum
across both species).}
\label{fig:patch}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{output/emergent.pdf}
\caption{Emergent size-distributions across a metapopulation.
Grey lines show patterns within individual patches differing in time since disturbance (age), with blue lines indicating patches of a specific age. Panels show (a) patterns of abundance, (b) leaf area and (c) height growth rate against size. Note that units of panels (a) and (b) are per unit height and per unit ground area. }
\label{fig:emergent}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{output/fitness.pdf}
\caption{Example fitness landscape for LMA, showing potential for stable
coexistence of multiple types.  Fitness is the log of the population growth
rate - at zero species are at equilibrium, above zero they will increase in
density.  (a) Landscape generated by a single species.  At LMA of 0.1 (the
dashed line) there is directional selection for smaller LMA.  At LMA of 0.08
(solid line) there is a branching point (see inset for more detail).  (b)
Landscape generated by two species, holing the first at LMA of 0.08.
Introducing a species at the maximum fitness value from panel (a) reduces the
region of positive fitness considerably (dashed line).  Dotted lines show
subsequent invasions and replacements of the second species, and the solid
line shows a stable fitness landscape where both species exist on a peak in
the fitness landscape.  At this point no further invasion is possible.}
\label{fig:fitness}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/plant.pdf}
\caption{Physiological dynamics for individual plants vary with size, trait
and light environment. (a) Growth trajectories for plants differing in light
environment and trait (LMA, low = 0.1, solid line; high =  0.267, dashed
line). Lower light environments slow trajectories and interact non-linearly
with traits. (b) Over time, the fraction of living tissue switches from leaf
towards sapwood, with high LMA species having relatively more mass in leaf
than low LMA species. (c) Growth rates peak around 5m high, but this position
varies with both trait and light level (note that this is the derivative of
panel (a)). (d) Growth rates vary with plant size (seedling and mature shown)
and with traits; growth rate differences are more pronounced in high light.
Whole plant light compensation points emerge from the model as the point where
growth rate is zero (x intercept).  The light level used in panels (a) and (c)
is indicated with dots.}
\label{fig:plant}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/patch.pdf}
\caption{Population dynamics for two species competing within a patch. Lines
in panels (a) and (b) show the growth trajectories for individuals on the
boundary of successive "cohorts" for each species. A single cohort includes
all individuals born within a given time period. Red lines are the low LMA
species from figure \ref{fig:plant}, blue lines are the high LMA species.  The
initial growth rate advantage of the low LMA species (see Figure
\ref{fig:plant} c) means it quickly over tops the high LMA species,
suppressing its growth.  Self-thinning leaves space for the high LMA species
to establish below the canopy of the fast species. Panel (a) shows all
trajectories equally weighted; the spacing is generated by an adaptive
refinement algorithm.  In panel (b) trajectories are shaded by the density of
individuals at given size and patch age.  (c) The leaf area index at ground
level for each species.  The dotted line is the total leaf area index (sum
across both species).}
\label{fig:patch}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/emergent.pdf}
\caption{Emergent size-distributions across a metapopulation.
Grey lines show patterns within individual patches differing in time since disturbance (age), with blue lines indicating patches of a specific age. Panels show (a) patterns of abundance, (b) leaf area and (c) height growth rate against size. Note that units of panels (a) and (b) are per unit height and per unit ground area. }
\label{fig:emergent}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/fitness.pdf}
\caption{Example fitness landscape for LMA, showing potential for stable
coexistence of multiple types.  Fitness is the log of the population growth
rate - at zero species are at equilibrium, above zero they will increase in
density.  (a) Landscape generated by a single species.  At LMA of 0.1 (the
dashed line) there is directional selection for smaller LMA.  At LMA of 0.08
(solid line) there is a branching point (see inset for more detail).  (b)
Landscape generated by two species, holing the first at LMA of 0.08.
Introducing a species at the maximum fitness value from panel (a) reduces the
region of positive fitness considerably (dashed line).  Dotted lines show
subsequent invasions and replacements of the second species, and the solid
line shows a stable fitness landscape where both species exist on a peak in
the fitness landscape.  At this point no further invasion is possible.}
\label{fig:fitness}
\end{figure}
